Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-05-15 paper/tidy-missing-data-paper.Rmd
render .bbl file

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      cache = TRUE)

library(tidyverse) 
library(gridExtra)
# options(kableExtra.latex.load_packages = FALSE)
# library(kableExtra)
library(ggthemes)
library(png)
library(scales)
library(simputation)
# if paper doesn't compile, use development version of naniar
# install.packages("remotes")
# remotes::install_github("njtierney/naniar")
library(naniar) 
library(knitr)
library(lubridate)
library(magick)
library(rpart)
library(visdat)
library(patchwork)
options(tinytex.verbose = TRUE)
```

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      cache = TRUE)
options(tinytex.clean = FALSE)
library(tidyverse) 
library(gridExtra)
# options(kableExtra.latex.load_packages = FALSE)
# library(kableExtra)
library(ggthemes)
library(png)
library(scales)
library(simputation)
# if paper doesn't compile, use development version of naniar
# install.packages("remotes")
# remotes::install_github("njtierney/naniar")
library(naniar) 
library(knitr)
library(lubridate)
library(magick)
library(rpart)
library(visdat)
library(patchwork)
options(tinytex.verbose = TRUE)
```
